---
title: "JOPSCIP Workshop"
description: |
  Digital Solutions for Research and E-portfolio!
site: distill::distill_website
output:
  distill::distill_article:
    css: style.css
    includes:
      in_header: password.js
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(distill)
library(htmltools)

# Include external CSS file
includeCSS("style.css")
```

<div class="workshop-intro">
## Welcome to JOPSCIP Workshop
### Digital Solutions for Research and E-portfolio

This workshop provides comprehensive training and resources for modern research methodologies and digital portfolio development. Our expert facilitators bring extensive experience in academic research and digital innovation.
</div>

## Meet Our Team

```{r team-profiles, echo=FALSE, layout="l-body-outset"}
# Create team section using simple HTML
div(class = "team-grid",
  div(class = "team-card",
    img(src = "images/temur_gugushvili.jpg", alt = "Temur Gugushvili", class = "team-photo"),
    div(class = "team-name", "Temur Gugushvili"),
    div(class = "team-title", "Senior Researcher & Workshop Facilitator", br(), "Digital Innovation Lab"),
    div(class = "team-links",
      a(href = "https://www.linkedin.com/in/temur-gugushvili/", target = "_blank", "LinkedIn"),
      a(href = "https://scholar.google.com/citations?user=XIuUIMwAAAAJ&hl=en&oi=ao", target = "_blank", "Google Scholar")
    )
  ),
  div(class = "team-card",
    img(src = "images/gvantsa_salukvadze.jpg", alt = "Gvantsa Salukvadze", class = "team-photo"),
    div(class = "team-name", "Gvantsa Salukvadze"),
    div(class = "team-title", "Research Coordinator & E-portfolio Specialist", br(), "Academic Technology Center"),
    div(class = "team-links",
      a(href = "https://www.linkedin.com/in/gvantsa-salukvadze/", target = "_blank", "LinkedIn"),
      a(href = "https://scholar.google.com/citations?user=O0k2rcgAAAAJ&hl=en&oi=ao", target = "_blank", "Google Scholar")
    )
  )
)
```

## Workshop Sessions:

- **Digital Identity**: Building Your Digital Academic Identity
- **Project Management**: Research Project Management & Communication
- **Literature Organization**: Reference Management & Literature Organization
- **Data Handling**: Data Collection and Analysis & AI-Enhanced
Literature Review

## Getting Started

Ready to enhance your research capabilities? Explore our workshop materials and connect with our team for personalized guidance on your digital research journey.

---

*For questions or additional information, please contact  on following email tgugushvili[at]ibsu.edu.ge, gvantsa.salukvadze[at]tsu.ge*